Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach

### 2021-02-10 Z_manuscript_for_correction_service/itt-emotion_first_half_V2_service.tex
Added first half correction from service

\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}

% Fold 1
  % Fold 2
    % Fold 3
      % Fold 4
        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}

        \author{Elisa Claire Alem\'an Carre\'on \protect\affmark[1] \orcidicon{0000-0002-6437-0866} \and
                Hugo Alberto Mendoza Espa\~na                                   \protect\affmark[1] \and
                Hirofumi Nonaka                                                 \protect\affmark[1] \and
                Toru Hiraoka                                                    \protect\affmark[2]
        }

@@

    %%%%%%%%%%%%% POSITIVE CHINESE ADJECTIVE PAIRS
    % Please add the following required packages to your document preamble:
    % \usepackage{multirow}
    % \usepackage{graphicx}
    % \usepackage{lscape}
    \begin{landscape}
    \begin{table}[p]
      \centering
      \caption{Top 4 words related to the mainly used adjectives in positive Chinese texts.}
      \label{tab:adj_zh_pos}
      \resizebox{\linewidth}{!}{%
      \begin{tabular}{|c|l|l|l|l|l|l|}
        \hline
        \textbf{Price range} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}大\end{CJK} (big)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}近\end{CJK} (near)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}新\end{CJK} (new)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great)}} \\ \hline
        \multirow{5}{*}{\textbf{0: All Prices}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 12892 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 9844 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 6665 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 5181 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 2775 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 3028 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 1462 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 3197 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 1224 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 453 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 363 &
          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 463 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 1426 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 772 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 737 &
          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 144 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 246 &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 218 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 869 &
          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 379 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 464 &
          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 122 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 116 &
          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 168 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 714 &
          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 232 &
          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 61 &
          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 108 &
          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 53 &
          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 164 \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}3: 5000 to\\  10,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 139 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 76 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 114 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 55 &
           &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 11 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 17 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 11 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 21 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 4 &
           &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 2 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 16 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 10 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 10 &
          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 2 &
           &
           \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 12 &
          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 5 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 6 &
           &
           &
           \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 8 &
          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 3 &
          \begin{CJK}{UTF8}{gbsn}干净 总体\end{CJK} (clean overall) : 4 &
           &
           &
           \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}4: 10,000 to\\  15,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 601 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 348 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 455 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 323 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 37 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 73 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 72 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 76 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 66 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 27 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 9 &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 6 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 37 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 30 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 52 &
          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 14 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 2 &
          \begin{CJK}{UTF8}{gbsn}棒 房间\end{CJK} (great room) : 3 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 34 &
          \begin{CJK}{UTF8}{gbsn}大 社\end{CJK} (big club) : 26 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 48 &
          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 12 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 2 &
          \begin{CJK}{UTF8}{gbsn}棒 水平\end{CJK} (great level) : 3 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 26 &
          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 16 &
          \begin{CJK}{UTF8}{gbsn}干净 打扫\end{CJK} (clean up) : 9 &
          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 10 &
           &
          \begin{CJK}{UTF8}{gbsn}棒 温泉\end{CJK} (great hot spring) : 3 \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}5: 15,000 to\\  20,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 1925 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1277 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1348 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1016 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 234 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 241 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 207 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 316 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 234 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 82 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 47 &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 33 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 168 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 140 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 35 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 25 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 131 &
          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 73 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 92 &
          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 34 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 22 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 109 &
          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 49 &
          \begin{CJK}{UTF8}{gbsn}干净 设施\end{CJK} (clean facilities) : 19 &
          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 29 &
          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}6: 20,000 to\\  30,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 3110 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 2245 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1940 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1433 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 517 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 440 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 409 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 680 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 360 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 164 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 89 &
          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 51 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 326 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 198 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 203 &
          \begin{CJK}{UTF8}{gbsn}近 地铁\end{CJK} (near subway) : 34 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 51 &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 45 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 206 &
          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 102 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 137 &
          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 31 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 24 &
          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 23 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 183 &
          \begin{CJK}{UTF8}{gbsn}大 空间\end{CJK} (big space) : 64 &
          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 21 &
          \begin{CJK}{UTF8}{gbsn}近 车站\end{CJK} (near the station) : 27 &
          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 10 &
          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 20 \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}7: 30,000 to\\  50,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 2291 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 1913 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1159 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 935 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 260 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 448 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 277 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 643 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 224 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 80 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 63 &
          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 68 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 274 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 141 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 146 &
          \begin{CJK}{UTF8}{gbsn}近 站\end{CJK} (near station) : 24 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 25 &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 34 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 140 &
          \begin{CJK}{UTF8}{gbsn}大 超市\end{CJK} (big supermarket) : 74 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 71 &
          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 20 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 15 &
          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 24 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 140 &
          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 66 &
          \begin{CJK}{UTF8}{gbsn}干净 环境\end{CJK} (clean environment) : 16 &
          \begin{CJK}{UTF8}{gbsn}近 山\end{CJK} (near mountain) : 12 &
          \begin{CJK}{UTF8}{gbsn}新 房间\end{CJK} (new room) : 11 &
          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 14 \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}8: 50,000 to\\  100,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 4451 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 3670 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 1577 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 1354 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 1634 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 1626 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 587 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 1340 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 310 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 88 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 141 &
          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 281 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 415 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 238 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 161 &
          \begin{CJK}{UTF8}{gbsn}近 桥\end{CJK} (near bridge) : 76 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 123 &
          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 112 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 328 &
          \begin{CJK}{UTF8}{gbsn}大 酒店\end{CJK} (big hotel) : 144 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 101 &
          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 35 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 57 &
          \begin{CJK}{UTF8}{gbsn}棒 位置\end{CJK} (great position) : 96 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 早餐\end{CJK} (nice breakfast) : 251 &
          \begin{CJK}{UTF8}{gbsn}大 商场\end{CJK} (big market) : 88 &
          \begin{CJK}{UTF8}{gbsn}干净 服务\end{CJK} (clean service) : 13 &
          \begin{CJK}{UTF8}{gbsn}近 铁\end{CJK} (Kintetsu) : 24 &
          \begin{CJK}{UTF8}{gbsn}新 斋\end{CJK} (new) : 22 &
          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 86 \\ \hline
        \multirow{5}{*}{\textbf{\begin{tabular}[c]{@{}c@{}}9: 100,000 to\\  200,000 yen\end{tabular}}} &
          \begin{CJK}{UTF8}{gbsn}不错\end{CJK} (not bad) : 375 &
          \begin{CJK}{UTF8}{gbsn}大\end{CJK} (big) : 315 &
          \begin{CJK}{UTF8}{gbsn}干净\end{CJK} (clean) : 72 &
          \begin{CJK}{UTF8}{gbsn}近\end{CJK} (near) : 65 &
          \begin{CJK}{UTF8}{gbsn}新\end{CJK} (new) : 77 &
          \begin{CJK}{UTF8}{gbsn}棒\end{CJK} (great) : 189 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 酒店\end{CJK} (nice hotel) : 53 &
          \begin{CJK}{UTF8}{gbsn}大 房间\end{CJK} (big room) : 131 &
          \begin{CJK}{UTF8}{gbsn}干净 房间\end{CJK} (clean room) : 9 &
          \begin{CJK}{UTF8}{gbsn}近 酒店\end{CJK} (near hotel) : 8 &
          \begin{CJK}{UTF8}{gbsn}新 酒店\end{CJK} (new hotel) : 19 &
          \begin{CJK}{UTF8}{gbsn}棒 酒店\end{CJK} (great hotel) : 36 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 位置\end{CJK} (nice location) : 30 &
          \begin{CJK}{UTF8}{gbsn}大 面积\end{CJK} (large area) : 19 &
          \begin{CJK}{UTF8}{gbsn}干净 酒店\end{CJK} (clean hotel) : 8 &
          \begin{CJK}{UTF8}{gbsn}近 地铁站\end{CJK} (near subway station) : 3 &
          \begin{CJK}{UTF8}{gbsn}新 设施\end{CJK} (new facility) : 13 &
          \begin{CJK}{UTF8}{gbsn}棒 体验\end{CJK} (great experience) : 10 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 环境\end{CJK} (nice environment) : 27 &
          \begin{CJK}{UTF8}{gbsn}大 床\end{CJK} (big bed) : 15 &
          \begin{CJK}{UTF8}{gbsn}干净 卫生\end{CJK} (clean and hygienic) : 5 &
          \begin{CJK}{UTF8}{gbsn}近 市场\end{CJK} (near market) : 3 &
          \begin{CJK}{UTF8}{gbsn}新 装修\end{CJK} (new decoration) : 3 &
          \begin{CJK}{UTF8}{gbsn}棒 服务\end{CJK} (great service) : 10 \\
         &
          \begin{CJK}{UTF8}{gbsn}不错 服务\end{CJK} (nice service) : 22 &
          \begin{CJK}{UTF8}{gbsn}大 卫生间\end{CJK} (big toilet) : 13 &
           &
           &
          \begin{CJK}{UTF8}{gbsn}新 位置\end{CJK} (new location) : 2 &
          \begin{CJK}{UTF8}{gbsn}棒 早餐\end{CJK} (great breakfast) : 8 \\ \hline
        \end{tabular}%
        }
    \end{table}
    \end{landscape}

    %%%%%%%%%%%%% NEGATIVE CHINESE ADJECTIVE PAIRS
    % Please add the following required packages to your document preamble:
    % \usepackage{multirow}
    % \usepackage{graphicx}
    % \usepackage{lscape}
    \begin{landscape}
    \begin{table}[p]
      \centering
      \caption{Top 4 words related to the mainly used adjectives in negative texts.}
      \label{tab:adj_zh_neg}
      \resizebox{0.7\linewidth}{!}{%
      \begin{tabular}{|c|l|l|l|}
        \hline
        \multicolumn{1}{|l|}{\textbf{Price range}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete)}} &
          \multicolumn{1}{c|}{\textbf{\begin{CJK}{UTF8}{gbsn}老\end{CJK} (old)}} \\ \hline
        \multirow{5}{*}{\textbf{0: All Prices}} &
          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 1713 &
          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 319 &
          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 297 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 137 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 184 &
          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 74 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 115 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 18 &
          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 58 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 106 &
          \begin{CJK}{UTF8}{gbsn}陈旧 房间\end{CJK} (outdated room) : 10 &
          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 15 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 97 &
          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 10 &
          \begin{CJK}{UTF8}{gbsn}老 装修\end{CJK} (old decoration) : 11 \\ \hline
        \multirow{5}{*}{\textbf{3: 5000 to 10,000 yen}} &
          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 28 &
           &
          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 2 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 5 &
           &
           \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 3 &
           &
           \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 味道\end{CJK} (general taste) : 2 &
           &
           \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 效果\end{CJK} (general effect) : 2 &
           &
           \\ \hline
        \multirow{5}{*}{\textbf{4: 10,000 to 15,000 yen}} &
          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 91 &
          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 34 &
          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 30 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 10 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 17 &
          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 8 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 位置\end{CJK} (general location) : 8 &
          \begin{CJK}{UTF8}{gbsn}陈旧 家具\end{CJK} (obsolete furniture) : 2 &
          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 6 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 2 &
          \begin{CJK}{UTF8}{gbsn}老 建筑\end{CJK} (old building) : 3 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 5 &
           &
           \\ \hline
        \multirow{5}{*}{\textbf{5: 15,000 to 20,000 yen}} &
          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 218 &
          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 43 &
          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 26 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 23 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 25 &
          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 11 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 21 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 3 &
          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 7 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 14 &
          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &
          \begin{CJK}{UTF8}{gbsn}老 外观\end{CJK} (old appearance) : 2 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 卫生\end{CJK} (general hygiene) : 8 &
           &
           \\ \hline
        \multirow{5}{*}{\textbf{6: 20,000 to 30,000 yen}} &
          \begin{CJK}{UTF8}{gbsn}一般\end{CJK} (general) : 504 &
          \begin{CJK}{UTF8}{gbsn}陈旧\end{CJK} (obsolete) : 75 &
          \begin{CJK}{UTF8}{gbsn}老\end{CJK} (old) : 55 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 设施\end{CJK} (general facilities) : 42 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设施\end{CJK} (obsolete facilities) : 42 &
          \begin{CJK}{UTF8}{gbsn}老 酒店\end{CJK} (old hotel) : 9 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 酒店\end{CJK} (average hotel) : 37 &
          \begin{CJK}{UTF8}{gbsn}陈旧 设备\end{CJK} (obsolete equipment) : 7 &
          \begin{CJK}{UTF8}{gbsn}老 设施\end{CJK} (old facility) : 8 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 服务\end{CJK} (general service) : 34 &
          \begin{CJK}{UTF8}{gbsn}陈旧 装修\end{CJK} (old decoration) : 3 &
          \begin{CJK}{UTF8}{gbsn}老 店\end{CJK} (old shop) : 3 \\
         &
          \begin{CJK}{UTF8}{gbsn}一般 早餐\end{CJK} (average breakfast) : 21 &
          \begin{CJK}{UTF8}{gbsn}陈旧 酒店\end{CJK} (outdated hotel) : 2 &

>>>>

\title{Differences in Chinese and Western tourists faced with Japanese hospitality: A natural language processing approach}
% Fold 1
  % Fold 2
    % Fold 3
      % Fold 4
        \titlerunning{Differences in Chinese and Western tourists faced with Japanese hospitality: ...}

        \author{REDACTED}

@@
